Towards a Wide-Coverage Grammar for Swedish Using GF

### 2012-01-03 doc/report/report.tex
slides

\begin{itemize}
\item
\textit{Pronominal object shift} is common in Swedish and obligatory in Danish and Norwegian.
\enumsentence{\begin{tabular}[t]{@{}*{11}{l@{\ }}}
a. & Jag & ser&  honom& \textbf{inte}&~~ & b.&Jag &ser &\textbf{inte} &honom\\
   & \emph{I} & \emph{see}&\emph{him}&\emph{not}&&& \emph{I} &\emph{see}&\emph{not}&\emph{him}\\
\end{tabular}}
%TODO Sats adverbials?
Personal pronouns are allowed to precede negation and some other adverbials of place --\textit{satsadverbial} --
in main clauses without auxiliary verbs.

>>>>

\begin{itemize}
\item
\textit{Pronominal object shift} is common in Swedish and obligatory in Danish and Norwegian.
\enumsentence{\begin{tabular}[t]{@{}*{11}{l@{\ }}}
a. & Jag & ser&  honom& \textbf{inte}&~~ & b.&Jag &ser &\textbf{inte} &honom\\
   & \emph{I} & \emph{see}&\emph{him}&\emph{not}&&& \emph{I} &\emph{see}&\emph{not}&\emph{him}\\
\end{tabular}}
%TODO Sats adverbials?
Personal pronouns are allowed to precede negation and some other sentence adverbials --\textit{satsadverbial} --
in main clauses without auxiliary verbs.
